### 2019-06-09 main-plos-singlefile.tex
plos one req

Ten of the patients were excluded from further analysis due to presence of
motion (n=2), severe susceptibility artifacts (n=5), or incomplete data (n=3).
The characteristics of the remaining 62 patients are shown in Supporting
Material (Table S1). Their median age was 65 years (range 45--73 years), while
the median serum PSA value was 9.3 ng/ml (range 1.3--30.0 ng/ml). The number of
patients having one, two, and three lesions was 29, 28, and 5, respectively.

@@

\begin{figure}[!ht]
    \centering
    %\includegraphics[width=1.0\textwidth]{figures/fig2}
    \caption{{\bf An example case with parametric maps.}
    A:~Whole mount prostate histological section.
    B:~ADCₘ (apparent diffusion coefficient, monoexponential model).
    C:~ADCₖ (apparent diffusion coefficient, kurtosis model).
    D:~K (kurtosis parameter, kurtosis model).
    E:~T₂w (T₂-weighted imaging).
    F:~T₂ (T₂-mapping).
    This is from patient \#43 (see Table~S1). The two lesions are outlined;
    their Gleason scores are 4+3 (lower, posterolateral region) and 3+4 (upper,
    anterior region).}%
    \label{fig:pmap}
\end{figure}

@@

Some of the top features were highly correlated between different image types.
See Table~S13 in Supporting Material for Spearman rank correlation coefficients
for the features listed in Tables~2 and~3, calculated across image types. In
addition, Table~S14 contains similar correlation metrics for all feature pairs,
where top five features were taken from each image type.

@@

The AUC values for the top-1\% texture features based on T₂w, ADCₘ, ADCₖ, K,
and T₂ are shown in Supporting Material Tables S2, S4, S6, S8, and S10,
respectively. Similarly, AUCs for the statistical features for each image
type are shown in Supporting Material Tables S3, S5, S7, S9, and S11.

@@

The final model proposed to differentiate low from high Gleason score PCa
includes the features from ADCₘ, K, and T₂w listed in Table~S12. The expected
performance ROC is presented in Fig~\ref{fig:roc}.

>>>>

Ten of the patients were excluded from further analysis due to presence of
motion (n=2), severe susceptibility artifacts (n=5), or incomplete data (n=3).
The characteristics of the remaining 62 patients are shown in Supporting
Material (S1~Table). Their median age was 65 years (range 45--73 years), while
the median serum PSA value was 9.3 ng/ml (range 1.3--30.0 ng/ml). The number of
patients having one, two, and three lesions was 29, 28, and 5, respectively.

@@

\begin{figure}[!ht]
    \centering
    %\includegraphics[width=1.0\textwidth]{figures/fig2}
    \caption{{\bf An example case with parametric maps.}
    A:~Whole mount prostate histological section.
    B:~ADCₘ (apparent diffusion coefficient, monoexponential model).
    C:~ADCₖ (apparent diffusion coefficient, kurtosis model).
    D:~K (kurtosis parameter, kurtosis model).
    E:~T₂w (T₂-weighted imaging).
    F:~T₂ (T₂-mapping).
    This is from patient \#43 (see S1~Table). The two lesions are outlined;
    their Gleason scores are 4+3 (lower, posterolateral region) and 3+4 (upper,
    anterior region).}%
    \label{fig:pmap}
\end{figure}

@@

Some of the top features were highly correlated between different image types.
See S13~Table in Supporting Material for Spearman rank correlation coefficients
for the features listed in Tables~2 and~3, calculated across image types. In
addition, S14~Table contains similar correlation metrics for all feature pairs,
where top five features were taken from each image type.

@@

The AUC values for the top-1\% texture features based on T₂w, ADCₘ, ADCₖ, K,
and T₂ are shown in S2, S4, S6, S8, and S10 Tables, respectively. Similarly,
AUCs for the statistical features for each image type are shown in S3, S5, S7,
S9, and S11 Tables.

@@

The final model proposed to differentiate low from high Gleason score PCa
includes the features from ADCₘ, K, and T₂w listed in S12~Table. The expected
performance ROC is presented in Fig~\ref{fig:roc}.
